\section{Barfoot Interrupts Himself}
I'm sorry for doing this, I don't normally interrupt the flow of a story, but I thought it was important to get this out here.

Not sure why I put so many love stories into that last section, maybe it had to do with my infatuation and falling out with Bob Graft's daughter, I don't know. I'm only 19, so perhaps I'm a little naive.

Before I began writing my additions to \emph{The Fall of King Mwe\-fu},
I had been writing Bob's daughter Anne a lot. And somehow, Bob invited me over for dinner one night; I had no idea the kind of mess I was about to find myself in.

I arrived at his house at 5:30pm, 30 minutes early so that I wouldn't be late. The house was in shambles, the soffits were hanging and dented, the fascia boards were rotted, and the hedges were unruly and were being overtaken by wild grapes and mulberries. Bob's wife Mary answered the old wooden door that was in need of a new paint job.

``Oh, you're early!'' She said flustered and slamming the door on me, ``Give me five minutes to finish tidying up.''

So I waited outside and cleaned up some garbage myself and found a rusty pair of loppers and began to trim the plants.

``What do you think you're doing!'' Asked Graft, sneaking up behind me.

``I'm just trimming some weeds.'' I replied.

``Those aren't weeds, those are valuable trees, the world is running short on trees.'' He shot back.

``I'm sorry. They didn't look wanted.'' I replied. He grabbed the loppers out of my hand and threw them back on the ground where I had picked them up from; then he led me inside. Bob was a man of 50 years, as was his wife.
The house was fairly messy, so I couldn't imagine what it had looked like before they cleaned it.
Bob sat me down at the table which was set for three and I could smell the spaghetti and Texas toast.

A loud mumble came from the other room. Bob twi\-tched in annoyance.

``Honey.'' Shouted Mary from the kitchen, ``Your dad wants you to help him to the kitchen.''
I thought that Mary was talking to their daughter Anne, but Bob spoke up.

``He was supposed to be napping.'' He said with agitation in his voice as he got up and went into the other room. He returned with his arm around a thin wrinkled old man. Bob sat the man down at the table and went to grab another chair and plate et cetera.

``You must be my future grandson.'' Said the old man.

``I don't know about that. So you're Bob's Dad?'' I replied.

``Step father.'' Said Bob interrupting the same as he scooted the old man and his chair aside so that there was room for himself to wedge a chair in.

``Tell me. Have you ever heard of a book called \emph{The Fall of King Mwe\-fu}?'' Said the step father.

``Now let's not bring this up, Al.'' Said Bob.

``Yes I have.'' I replied, ``It's a great story.''

``Ah yes.'' Said Al grinning, ``But which is your favorite translation?''

``I've only read the original.'' I said.

``The original Fobwa?'' Asked Bob seeming to lighten up.

``No. The Pa\-co\-itz translation.'' I said, ``I tried the other translations, but I could never get into them.'' Al smiled at this answer and Bob's countenance sunk.

``Why must you do this?'' Said Mary setting the pot of spaghetti down on the table, ``Can we please talk about something else? Especially when we have company.''

``Oh come on. I hear that I'm all that Bob talks about at work.'' Said Al.

``No, I didn't even know he had a stepdad.'' I said.

``I'm Allen G. Pa\-co\-itz. I was the first to discover and translate \emph{The Fall of King Mwe\-fu}.'' Said Al.

``Oh.'' I replied, ``Then yes he talks about you, but he's never told any of us that he \emph{personally knew you,} let alone that you lived in his house and were his stepdad.''

``My house.'' Said Al, ``Yep, that's funny, Bobby is such a hoot. I'm not sure who has more shame though, him of me, or I of him.''

``You're insufferable.'' Said Bob.

``Don't mind Bob, that's his little mind's way of saying that he loves me.'' Said Al.

``Why did you have to ruin a great work of literature by doing such a poor job translating it?!'' Said Bob.

``I made it better. Charlie agrees with me.'' Said Al, ``Now would someone go get some apricot jam please?'' I got up to look for some jam in the refrigerator, but Bob stopped me.

``No!'' Said Bob, ``You can't let him put jam on cheesy garlic bread. Those flavors absolutely cannot go together.''

``It all mixes in my stomach anyway.'' Said Al as I handed him the jam. He poured nearly the whole jar on his Texas toast. Mary, Bob, Al, and I all sat down and bowed our heads to pray.

Bob prayed: ``Thank you \emph{heavenly} father, for this food. Thank you that the people who translated your word were faithful and did not rewrite it. Thank you for Charlie who always does a great job at work and sometimes sticks up for me. Thank you for my beautiful wife that cooked the food, but sometimes she abandons me. God, change the hearts and minds of all of those people that are deceived, show them the truth. I pray for all those teachers who have made people suffer throughout the ages, teaching literary elements and nonsense instead of teaching integrity and truth. God, bless myself. Bless president John Fitzgerald Kennedy, keep him alive for many years. This might be beyond your power, but forgive my step-father for ruining literature for all of time. Forgive Charlie for killing all the trees and turning the planet into a desert. Forgive my wife for under--''

``Amen! Amen!'' Said Mary interrupting Bob's prayer, ``Honey, you know we were talking to God, right?
Because it sounded like you were trying to criticize us.''

``I'm thankful, and asking for forgiveness for all of you. Didn't you hear my prayer?'' Said Bob.

``It was condescending.'' Said Mary.

``It's really hard not to be condescending when you really are better than everyone else.''

``Why don't you write something of your own then?'' Said Al.

``Ha, you've never written anything, you've just corrupted things.'' Said Bob.

``Actually --'' Said Al sounding as if he was about to confess to something.

``I don't want to hear it.'' Said Bob interrupting.

``Bob, you need to forgive.'' I said nervously, ``Jesus has forgiven you, pass it on.''

``I have! But I'm not stupid. Fool me once, shame on you, fool me twice, shame on me.''

``Jesus said we should forgive people 70 times seven times.'' I said.

``Oh believe me, I've surpassed that number years ago.'' He said.

``Love keeps no record of wrongs.'' I said.

``Love takes two people.'' Said Bob.

``Jesus loves even those who don't love him back.''

``I'm not Jesus.''

``But you should be. That's what being a Christian means.''

``Charlie, I think you're getting too religious. You're so heavenly minded you're no earthly good.''

``Bob. Do you want me to apologize for focusing on things that matter instead of things that don't?''

``Sometimes Bobby gets bogged down by details that don't matter.'' Interjected Al.

``But they do matter,'' Said Bob, ``Big pictures are made of an orchestration of little details. When those details are out of place, like those puns and errors that you put into your translation, it spoils the whole work.''

``To the victor belong the spoils.'' Said Al.

``This isn't the way to act around company. Both of you, be quiet.'' Said Mary, ``Let's enjoy our food.'' There was an awkward silence for a couple minutes as we quietly ate our food.

``Hey, umm\ldots Is Anne coming to eat?'' I asked, breaking the silence.

``Who's Anne?'' Said Mary.

``Your daughter?'' I said slowly.

``We have no daughter.'' Said Bob. I could see Al's face strain.

``Oh, my heart. It's not doing well, I think I'm having a heart attack.'' Said Al his face turning red.

``I hope it's real this time.'' Said Bob.

``Bob!'' Said Mary rebukingly as she rushed to her father-in-law's side.

``In the name of Jesus, be healed.'' I said, putting a hand on Al's shoulder.

``My back was aching,'' Said Al looking well, ``but now it feels better.''

``And your heart?'' I asked.

``Oh! It's still bad. Just leave me be.'' Said Al as he twitched and squirmed. I reached out to pray for him again.

``Don't pray for me!'' He said, ``I'm having a heart attack beyond the power of Jesus to heal. I think he wants me to have it.''

``That's not what a heart attack looks like.'' Said Mary.

I spoke up: ``Jesus is the one `Who forgiveth all thine iniquities; who healeth all thy diseases;' Jesus died not only for our sins, but to heal us, they go hand in hand.''

``I say we let him die.'' Said Bob.

``He fakes this kind of thing all the time when someone asks him a question he doesn't want to answer.'' Said Mary.

``Fine. You got me.'' Said Al sitting up straight again.

``I can't remember asking him a question.'' I said, ``Does this have anything to do with Anne?''

Al started flailing his arms and complaining about his heart again.

``Allen Geoffrey Pa\-co\-itz!'' Said Mary, ``Stop it!''

Al burst out laughing, and Bob joined him.

``Dad, please tell me you didn't.'' Said Bob between chuckles.

``Allen!'' Said Mary, ``You wrote this poor boy love letters pretending to be a daughter that I don't have? Is that your idea of a joke?!''
 I buried my head in my hands in shame, realizing what had happened.

``Honestly, I thought he'd find out sooner. I had no idea it'd last this long.'' Said Al.

``Why in the world would you do that!?'' Demanded Mary.

``I was bored. Bobby took away all my notebooks, all I had left was some scrap pieces of paper to write on. So I wrote shorter things, and I found Charlie's address on a note that he wrote so that Bobby could pick him up for work that one time. So it just sorta happened, I can't control my creative urges.''

``That's why you've insisted on getting the mail every day then.'' Said Bob shaking his head between chuckles.

I got up from the table in shame and left; Mary tried to stop me, but I didn't appreciate being the butt-end of a joke like that. I forgave them all quickly, but finding that manuscript in the trash was surely a divine opportunity to play a little joke back.

I'll get the last laugh in the end; not that I'm bitter or anything.
