\section{Rushing Wind}

King Seaweed began his work of helping rebuild Zinodwo, he went out and he joined the royal building crews and they fixed up people's homes. But the people yelled at the king and tried to kill him to no avail.

``I hate you! You're a very wicked selfish king.''
Said a young man holding a sign that said, \emph{``Death to all tyrants!''}

``That's fine.'' Said the king as he gave the man an orange. But this made the man even madder, ``Don't you care what I have to say?!''

``Not really, but go ahead.''

``The tribute of Kaaji has stopped and you've made us all poor!''

``Would you like a job? I'm sure I could find something for you to do.''

``No I don't! I need the income that Mwefu used to give us.''

``I thought everyone hated Mwefu.''

``We did, before you came along. I'd give anything to have him back.''

``Maybe I'll give him a job then.''

``If you like him, then you're both tyrants. Death to you both.''

\tbreak

``When are they going to execute you?'' Asked Seaweed.

``It's strange.'' Said Mwe\-fu, ``I have no idea.''

``They postponed your execution so that you could kill me.''

``It seems to be. That doesn't bother you at all?''

``If it's my time to die, it's my time to die.''

``I don't understand it.'' Said Mwe\-fu, ``You were able to leave your old life of sorcery and treachery and move on, but my past is always going to haunt me and I can't commit myself to a side.''

``Of course you can't.'' Said Seaweed, ``If you're fighting yourself you're going to lose. Or at best you'll be stuck at a stalemate. You are your own equal, fighting yourself is unwinnable on your own, you need help.''

``Even if I could stick to a side, I've still lost everyone's trust. I want what you have, that spirit that gives you power and peace.''

``There's only one way.'' Said Seaweed, ``You have to recognize that when you killed the traveler that we all died with him.''

``What does that even mean?''

``When he died, he took all your evil upon himself, just as he took mine.''

``And if you recognize that, and confess that the Traveler is Lord, and believe that he rose from the dead, you'll be saved. Saved from yourself, and brought into life forever.''

``The Traveler is Lord, he's risen from the dead and now he lives in you.''

``Ok.'' Said Seaweed touching Mwe\-fu on the shoulder, ``Now he lives in you as well.''

``That's it?'' Said Mwe\-fu, ``Nothing happened. I don't feel any different.''

``Why would you feel any different?''

``I just thought that I'd feel a sensation or something.''

``Walk by faith. Not by sight. If you rely on your feelings to guide you then you're going to be in trouble.''

Seaweed got up and started walking east.

``Where are you going?'' Asked Mwe\-fu.

``To the sea.'' Said Seaweed

``Why? Can I come?''

``To get a ship. If you know who you are then nothing is impossible for you.''

``I'm Mwefu, a worthless fugitive who --'' Said Mwefu right before 
Seaweed interrupted him and slapped him to the ground.

``-- No.'' Said Seaweed, ``That's who you were, but Mwefu died. Now you're a son of God.''
