\chapter{Charles Barfoot's Continuation}
\section{Conspiracies}
I found Bob Graft's additions (Appendix C and D) crumpled up in the trash. I don't think he wanted anyone to read them, but wouldn't it'd be funny if they somehow ended up in the finished book? Bob is never going to read this book anyway, so I can probably get away with almost anything.

I'm going to pick up where Bob left off, but there's going to be some significant differences:
\begin{enumerate}
\item I don't care about texts, languages, footnotes and other irrelevant distractions from the story.
\item I care about the story. Bob's idea of a good story is the dictionary.
\item I have no idea what is supposed to happen next in the story, but I'll just do my best to make up something interesting. You may not like it, that's your right.
\end{enumerate}

\begin{flushright}
\textsc{
Charles Barfoot,\\
Janitor of \emph{Whinery Press}}
\end{flushright}

Captain Seaweed lumbered towards the throne and sat himself down on it.
``I'm the king now," He said, ``any questions?''

The old king, who I'll call Kevin, rallied the soldiers to attack king Seaweed.

``Seaweed is going to stop the Kaaji tribute and leave this nation poor!'' Said Kevin.

``Captain Seaweed is a ruthless man who killed lots of innocent people and conspired against the country. He actually makes Mwefu look innocent.'' Said Twizwa.

``That's fair.'' Said King Seaweed, ``But I'm not the same person I was.''

``You're right, you're old and washed up --'' Said Kevin.

``Was that supposed to be an insult?'' Interrupted Seaweed, ``Because I beat all you easily. What does that make you?''

King Seaweed stood up and four guards rushed towards him and lept upon him; but Seaweed threw them off and entered his palace.

``Something is going on here.'' Said Kevin, ``There's no way he could beat me in a fair fight.''

``He just brushed off four fighting men like they were nothing.'' Said Twizwa, ``That's not natural skill. Some kind of evil is afoot inside him no doubt. I propose the four of us (Kevin, Mwefu, Naazwato, and myself) team up to take him down before he ruins everything.''

``It only took you three men 12 seconds to go from patriots to traitors.'' Muttered Mwefu.

``Touch\'{e}. So you're on our side?'' Said Twizwa.

``Might as well.'' Said Mwefu.

``Still can't believe you were Mwefu the whole time.'' Said Naazwato.

\tbreak

So the quartet schemed and set out to assassinate the king. Twizwa still had his position as second in command, so he convinced the cup bearer to poison king Seaweed.

\tbreak

Twizwa watched as Seaweed guzzled down a glass of wine. ``Trevor, this is an excellent drink, what did you put in this? It tastes wonderful.'' The king said as he handed the remainder of the glass to his cup bearer.

``Take a sip, it's got quite a kick to it.'' Seaweed suggested. Trevor was confused, but thinking he had accidentally developed a novel wine instead of poisoning the king as he had hoped, he took a drink. But Trevor had not made a mistake, it was indeed poisoned; he convulsed and died. 

``Trevor! Are you alright? What have I done?!'' Cried Seaweed, ``How was I supposed to know that it'd be too strong for you?'' Twizwa ran up to the corpse and confirmed that he was indeed dead.

Seaweed, however, picked Trevor up and slapped him. Life shot back into the cup bearer's face as Seaweed told him to be more careful. 

Because that plan failed, Twizwa met secretly with Mwefu, Naazwato, and Kevin. He told them what happened.

``Was the poison faulty?'' Asked Mwefu.

``No.'' Said Twizwa, ``That was the finest poison in the greatest quality. No one could have survived it.'' 

``Perhaps he was immune.'' Said Naazwato.

``You're so naive, it doesn't work that way. That would be like saying that he's immune to beheading.'' Said Twizwa.

``But Trevor survived a small sip.''

``No! He was dead.''

``Then what happened?!'' Asked Kevin.

``Power must have went out of Seaweed and into the cup bearer when he slapped him.'' Said Twizwa.

``I doubt it.'' Said Mwefu, ``Everything can be explained in the natural. Snakes are a much more reliable deliverer of venom.''

So they bought ten different kinds of venomous snakes and Twizwa let them out in the king's bedroom while he was sleeping.

The next morning Twizwa went to see if the king was dead. Twizwa was wearing full armor so that none of the snakes could bite him. The king wasn't breathing. Twizwa moved closer to be sure he was dead; but the king twitched, snorted, and started snoring. Twizwa pulled back the covers to find the ten snakes cuddled up with the king but it didn't look like any had bitten him. So Twizwa shook the king's bed and said, ``King Seaweed! Some fiend has put venomous serpents in your bed!'' A loud slithering could be heard and the king got up and let out a few cries.

``Darn snakes.'' He said getting out of bed. All ten snakes were latched onto his body and he shook them off, and lifeless they hit the ground.

``Good thing you're wearing armor.'' Said Seaweed, ``You could have been bitten, let me tell you, it stings.''

``You'll probably die.'' Said Twizwa sitting down in a chair as Seaweed got up and put on his kingly robes.

``If I could be so lucky.'' Scoffed the king taking no mind of it. He walked to the throne room and sat on his chair and began reading through piles of reports and notes.

``We have to do something about the beggars, Twizwa.''

``Give them more money.'' Said Twizwa.

``If only it were that easy. A dependence on other people's labors makes them lazy so they don't value the money and they waste it on frivolity. We need to encourage working and craftsmanship.''

``You just don't want to give them the treasure. Where's your heart?''

``I don't know, how 'bout you go find it while I get some work done.''

So the king went out to tour the kingdom while Twizwa stayed behind and studied.

\section{Captain Seaweed}

Twizwa read some books on astronomy, astrology, aardvarks, and finally he got to one about the kings of Zinodwo.

Here's the part he read about Captain Seaweed:

\begin{quote}

As a boy, Sarnu was going by ship to the Indies with his parents when they got shipwrecked on an abandoned island. His father and mother tamed the wild island and it became quite hospitable, but still they died of disease eight years later. Eventually another man got shipwrecked and washed ashore to the island where Sarnu lived. His name was Max, and fortunately for Sarnu, he was an expert shipbuilder. Max was a man of perhaps 50 years, and Sarnu was now 17, and together they built a boat to make it to a populated island. From there they hired a crew and built a bigger boat which they could use to ship spices and goods.

Sarnu had a good head for numbers and good arms and back for labor. Max made Sarnu his partner and together they built ten ships and amassed a good deal of profit. Max never called him Sarnu though, he was known only as Captain Seaweed.

After a dozen years, Max died in a shipwreck; so Seaweed sailed back to Zinodwo to see how his people were faring. He saw that the people there were lacking in leadership and were being destroyed by the Kaaji.

``Ahoy.'' Said Captain Seaweed to the people, where is your king?

``He's dead.'' Said a young woman, ``They're all dead. The royal bloodline is broken.''

``I am a busy man.'' Said Seaweed, ``But I'll help the country out for your sake.''

So Seaweed and the crew of nine of his ships drove out the Kaaji who had taken over Zinodwo and they killed all the bandits and murderers. Seaweed declared himself king and every one agreed that he was the best king they had ever had.

He married that young woman, whose name was Heidi, and they had seven children.

He eventually stepped down from his throne and instituted a law that said that the winner of the tournament shall be king.

\end{quote}

Twizwa read the above to his companions.

``Those are all lies.'' Said Kevin, ``I've heard stories of what he actually was like. They say he practiced witchcraft, sold his soul to some demon or something. They say that he actually killed the royal family.''

``I've just received word back from the pirates that Seaweed ruled.'' Said Naazwato, ``They said that he is most definitely not Captain Seaweed.''

``What makes them so sure?'' Asked Mwefu.

``Seaweed has been dead for over 20 years.'' Said Naazwato, ``They said they'll pay me 30 pieces of 8 if I bring him to them.''

``Why would they want him if he's a fake?'' Said Kevin, ``Sounds like they're a little sour that their captain abandoned them.''

``Or they don't want his name sullied by old washed up bums.'' Said Mwefu.

``He beat all of you. He's defeated all of us, maybe he's not as innocuous as he seems.'' Said Twizwa.

\tbreak

The next day, Naazwato went to the iron hills. He came across a mud hut with a lion skin entry rug. He whistled a tune and spoke an incantation that opened a hidden door beside the hut.

``What need have you of a sorcerer, Naazwato?'' Said an old thin man who stepped through the door. He was perhaps 70 years old and was dressed in hippopotamus leather.

``Zinodwo has been taken over by an evil sorcerer I do believe.'' Replied Naazwato.

``Captain Seaweed is nothing compared to the power I have. Give me a sheep, some of his hair, and your shoes, and I will take care of him.'' Said the sorcerer.

So Naazwato went out and got these things and returned and gave them to the man. The sorcerer then made a magic wand, but kept the shoes out of it.

``What did you need my shoes then for? Those were brand new, beautifully hand crafted by the most lovely woman in Zinodwo.'' Said Naazwato.

``I need them for payment. I don't work for free.'' He replied.

So they went to the palace to kill the king and found him in his throne room organizing papers.

``Do you have an appointment?'' He asked, not even looking up.

``I'm an old friend come to take your life.'' Said the sorcerer as he raised his wand to smite king Seaweed, but nothing happened. He waved it again and tried various incantations but still nothing happened.

``What have you done to my magic!?'' The sorcerer cried as two guards carried him out. Seaweed said not a word, but looked up and smiled.

\tbreak

The next after, Kevin was out robbing civilians when the old woman he was robbing managed to catch him in a trap. She taunted him through the net that was now hanging in her kitchen with a former king in it.

``Sonny.'' She said, ``Can't you lose gracefully, you go from king back to thief in the matter of a few days. I really hope Oscar doesn't find out.''

``Who's Oscar?'' Asked Kevin.

``Oscar Seaweed. He's king now I hear.''

``Did you know him?''

``Only intimately. He was my husband.''

``What happened?'' Asked Kevin as the woman handed him a cup and saucer of tea.

``Well.'' The woman began her story:

\begin{quote}
My name is Rebekah. I was just a young woman at the time. I was 20, and I was making food for the less fortunate. Oscar Seaweed was a man of 22, and when he got off his ship he was instantly smitten with me. He loved me dearly, and I loved him. He had his ships bring many fish and spices and he and I cooked up a tremendous meal together. After a month or two of flirting, he finally asked me to marry him. My father was a bad judge of character, so I accepted.

Noticing that he was a smart man with lots of ambition, I suggested that he try to fix the kingdom since the royal family was wiped out. So he formed an army and kicked out Zinodwo's enemies and the people made him king.

I gave birth to his daughter, we named her Edith.

But I soon found out that Oscar wasn't the good natured merchant he seemed to be. He had a mean side to him, and his ships dealt in illegal contraband. That didn't bother me as much as his infidelity. I sneaked into his ship's cabin one day while he thought I was away; there I saw him with three or four woman hugging his arms. As soon as he noticed me there, the other women vanished.

``Bekah.'' He said, ``I love you.''

``I don't feel loved.'' I said.

``But you know I do.'' He replied, ``I know those other women must bother you, but they weren't real. I'm wholly devoted to you.''

``You made a commitment to me. And I made a commitment to you. To give ourselves to none other but each other.''

``And I haven't.'' He said.

``But you have. You love your witchcraft and yourself more than you love me. Aren't I enough?'' I cried bitterly.

\end{quote}

``Sorry,'' Said Rebekah in between her fits of sobbing, ``I don't usually share this story, especially not with thieves in my kitchen.''

``Please go on.'' Said Kevin with a tear running down his cheek.

\begin{quote}

Well\ldots

``Maybe the truth is that I don't feel like I love you anymore.'' Said Oscar.

``How could you not love me? What happened?'' I asked.

``I just don't have that stirring in my stomach around you anymore.''

``That isn't love. Love isn't a feeling! Love is a bond of will towards another person. To be one and undivided.''

``You said before that you didn't `feel loved.''' Said Oscar.

``That's different. I don't feel loved because you always put everything else before me. I've been giving all of myself for you. You're supposed to give all of yourself to me.''

``You sound jealous.'' He said.

``I'm supposed to be jealous, I'm your wife. How can anything else compare to my love for you? I'm right here.''

``Maybe you should stay there.'' He said as the tears ran down his face as well.

I left with Edith and I haven't seen him since. I keep hoping he'll come back. I've never remarried, his ring is still on my finger. I know he'll never change, but I love him anyway.

\end{quote}

Kevin looked at the ring, it was the finest ring he had ever seen, a fine work of gold, silver, and numerous precious stones.
``That would fetch a great price.'' He said.

``Take it. I've given up. I don't want to be reminded anymore about how he broke my heart. I put so much in, and all I have to show for it is that ring.''

So Rebekah let Kevin go and handed him the ring.

``If you find yourself a wife, don't abandon her.'' She said.

\tbreak

``I'll kill him when he's sleeping. Slit his throat.'' Said Mwefu.

So while Seaweed slept that night, Mwefu sneaked in through the secret passage way and swung his sword at Seaweed. The slice went through his neck and sliced into the mattress sending feathers everywhere. Captain Seaweed then sneezed and got up.

``Mwefu, what are you doing to my bed?'' Said the king.

Mwefu swung his sword again but it was grabbed by an ethereal glowing hand which seemed to come out of the king's stomach. The apparition vaporized the sword and it too disappeared.

``What kind of witch craft have you been meddling in?!'' Demanded Mwefu.

``I really ought to kill you.'' Said Seaweed, ``But since you once had mercy on me, I will have mercy on you. I will also tell you what you want to know.''

\begin{quote}
What you read about me in the chronicles of the kings wasn't true. I made it up to cover who I really was.

I was a boy named Oscar who grew up in Zinodwo. My aunts were witches and they raised me and taught me to meddle in dark powers. I used that power to take over ships and kill anyone who stood in my way. I traveled all around the world amassing a collection of seven ships which I had stolen from their previous owners. I used them to smuggle spices and to demand tribute from lesser lands and islands. I become very wealthy but I was not very happy.

Then I returned back to Zinodwo. Behold, I saw a beautiful young maiden making flour and preparing a large feast.

``What are you doing?'' I asked.

``I'm making food for he poor of the kingdom.'' She replied. Something stirred in my heart, so I helped her. I sent my ships out and they brought back thousands of fish and various exotic spices. The meal was so extravagant that the royal family was offended that the food was given to beggars and not to them. The king tried to have me killed, but I used my dark powers to kill him and his family, every last one.

I didn't let that young woman, whose name was Rebekah, know that I had slaughtered the royal family. I loved her dearly and begged her to marry me, and she did. I made myself king, but it wasn't enough.

``Oscar,'' Rebekah said, ``I thought you loved me. Why is it that you still perform witchcraft and are always away?''

``I have important things to do.'' I replied.

``I made a commitment to you. And you made one to me, to be wholly devoted to one another, but your heart seems to be elsewhere.''

``The feeling of love went away soon after we were married.'' I said.

``Love isn't a feeling.'' She replied, ``You don't base your relationships off of feelings, you're supposed to do it based off of your strength of will.''

``Alright.'' I said, ``I'll spend more time with you.''

So I did, I spent more time with her, but still she was distraught.

``I've noticed you conjure up apparitions of other women. I thought you loved me.'' She said.

``I do love you. It's not like they're real women, it's just a little entertainment for myself.''

``I don't care who or what I share you with, I want all of you.''

``If you can't deal with me, maybe you should leave.'' So she left, and I felt the absence of her love. I realized that she was the only good thing in my life. But I was free now. I could do whatever I liked, and so I did. I abandoned the throne, it was too much work anyway, and made the winner of the tournament the next king.

I traveled around again, this time finding witch doctors, psychics, and sorcerers. I learned their tricks and engaged in their rituals, I was determined to be the most powerful sorcerer.

The crews of my ship became increasingly wary, as I became increasingly agitated. One day, we landed at Kaaji, and I went for a walk in the graveyard.''
\end{quote}

``Did you encounter the beast?'' Asked Mwefu, ``Is that how you got your scars?''

``Actually yes.'' Replied King Seaweed.

\begin{quote}
I saw a thousand shadows walking about with no owners. ``Come to me!'' I cried, ``I'll be your master.''

``You don't own us, we own you.'' They said as they grappled onto me. I could feel their power melding with my own. But I was still empty, even more empty. I transformed into a giant beast monster and demolished all life that was in the valley. They now call it the desecrated valley.

My crew built a cage to try to keep me contained, but my power was greater than theirs, I swallowed many of them whole. I was in agony and spent my days cutting myself with gravestones and rocks to try to distract myself from the pain inside me. I tried to die, but I couldn't.
\end{quote}

``So you were the monster we killed.'' Said Mwefu.

\begin{quote}
Not exactly. I saw you two approach that day, I picked you both up and beat you around. I was going to eat you, but someone greater than I appeared. I knew who he was, though I had never met him, the voices told me he would kill me, that he alone could kill me.

``Suffer me to live.'' I cried.

``I'll suffer you to die.'' He said as his spirit within him leapt out and rent my spirit in two. I was now freed from the evil spirits I had accumulated my whole life, in a flash I was made new. He gave me a hug, and I felt my heart that once was stone beat with love.

``You've saved me from myself.'' I said.

``He's not defeated yet. I have to become you, so you can become me.'' Said the man. He transformed as I had, and I knew how much pain he was in. Only, I had deserved it, I wanted it, I earned it, but this man was perfect, he had not committed a crime, yet he took on my evil which was repulsive to him.

``Maybe we can kill this one.'' Said Naazwato.

``But he's not a monster, he saved that man by taking his place--''

``He may have not been before, but he is now, someone ought to put him out of his misery before he slaughters anybody.''

So you two beat him with swords and he used every ounce of willpower not to fight back. I knew he could have killed you even by accident with that much evil and power flowing through him. Finally, after many blows, he was near death. The sun stopped shining, and the earth got cold. Then the sun came back, and the man who saved me was dead, the beast was no where to be found, only the body of the man.

``Wrap the body, we're taking it to Zinodwo.'' Said Naazwato.

You could have killed me, I was the beast, but you let me live.

After you two left with the body, I went back to my cage. I was there for two days, crying day and night.

The gravedigger approached me.

``What are you doing.'' He said.

``I'm staying here where I belong, I'm a monster. I've killed countless people.''

``I've heard of the beast that lives in the desecrated valley, but you're not him.''

``Maybe not, but I used to be.'' I replied.

``What happened?''

``A traveler came by, he took the monster spirit off of me and he put both himself and the spirit to death.''

``The beast is dead then.'' He said, ``Why are you still living as if he were alive?''

``It's my fault, I should have been the one to die, I --'' Then the gravedigger reached out his hand and a flaming white ghost stepped into my body.

``It's you! You're alive.'' I said, recognizing him as the traveler who rescued me.

``Yes. I wouldn't let death separate us.'' He replied. ``I gave all of myself for you. But in order for you to have peace, and joy, and faith, and self-control, you'll have to give all of yourself to me. You're my son now. You can have my spirit. It's stronger than whatever you had before, don't turn back, the old you is dead.''

``Sounds like marriage.'' I said.

``I know you didn't do so well at it. You've tried everything the world had to offer, be my son, I won't ever let you down.''

This wasn't a regular man, he had absolute power. He had control over nature and all supernature, he was God himself. There's many multitudes of people on this earth, but he took time for me, and if he can do that, he has time for you as well.

\end{quote}

``You're saying that you have the spirit of a god in you?'' Said Mwefu.

``Not \emph{a god}, \emph{THE GOD}. He directed me here, and I felt his spirit move me to enter the tournament, so I did.''

``Can you perform some magic or something so I know you're telling the truth?''

``You mean apart from all your failed assassination attempts?'' Said the king.

``Sure.''

``God healed the beggar before the tournament.'' Said Seaweed.

``He can walk now?'' Said Mwefu.

``He can. He just chooses not to.''

So Seaweed took Mwefu out and they found the beggar.

``The king says you can now walk.'' Said Mwefu.

``He's got you bewitched. That sort 'o thing is impossible.'' Said Bwaa.

``If he doesn't choose to embrace his new life, it won't affect him.'' Said the king.

``He really is a conman. He's fooled e'ry one but me.'' Said Bwaa.

So Mwefu went to Twizwa's house and Seaweed went back to his palace.


\section{The Ring}
The next day, Kevin went to see king Seaweed, and he managed to get an audience with him.

``How much would you give me for it?'' Asked Kevin holding up Rebekah's ring.

``Where did you come by that?!'' Said Seaweed.

``A woman gave it to me. She said her name was Rebekah, she said she was your wife. But the chronicles said your wife's name was Heidi.''

``The chronicles are a lie, I'm sorry. Heidi wasn't real, Rebekah was my real wife.''

``A pound of gold for this ring.'' Said Kevin.

``Take it. Add it to the 20 lbs you've already stole.'' Said Seaweed as he snatched the ring out of Kevin's hand, ``Where is Rebekah now? I need to see her.''

``She lives in a house on the eastern shore, I can show you.'' Said Kevin.

So Kevin took king Seaweed to the house and left Seaweed to face Rebekah on his own.

``Bekah!'' He shouted, as he entered the tattered wooden shack. But he soon found himself caught in the same trap that earlier had caught Kevin.

``Who are you!?'' Said Rebekah as she held out the point of a spear toward the hanging king.

``I'm an unworthy worm who has been unfaithful all these years.'' Said Seaweed, holding out the ring.

``Oscar, you came back. After all these years.'' Said Rebekah.

``How is our daughter?''

``She's a grandmother now.''

``I'm sorry I missed the life we could have had together. I'm sorry that I was never there for you. I'm sorry that I never loved you.''

``I still love you. I've never so much as looked at another man.''

``I've been so wicked, there was never anything in me worth loving.''

``Even so. I love you.'' She said.

``You were right about everything.'' Said Oscar.

``Stop it. You know I love it when you say that.''

``Every woman does.'' He said.

``What do you know about other women?'' She asked.

``More then I'd like. Nobody can replace you. Well, I do have a commitment that might get in the way.''

``You've remarried?'' Asked Rebekah beginning to cry.

``No. My thirst for power turned me into a literal monster and I killed many people. But I was rescued by God himself, he took my place and died and came back. So I've given my life to him, there may be room for you, but you'd be second.''

``\emph{EVERY SINGLE TIME.}'' She muttered, ``Don't you \emph{EVER} come back unless you have the will to put me first.''

``I'm amazed at how you put up with me. But I'm a different person now. I've learned to love, and it's because of God, and I want to give him all of me.''

``You do that.'' Said Rebekah as she let Seaweed down and motioned him out the door. She weeped quietly, and Seaweed groaned within his spirit.

\tbreak

Later that day, Mwefu and Seaweed were once again talking to one another.

``Have you ever loved a woman Mwefu?'' Asked Seaweed.

``Yes I did.'' Said Mwefu, ``She was amazing, she was smart, beautiful, hard working, talented artisan, wonderful fighter even.''

``Did you marry her?''

``No, we were engaged, but she drowned after saving a child from the river.''

``So you've never found anyone else?'' Said Seaweed.

``No.'' Said Mwefu, ``No one else could possibly measure up to her. I loved her dearly, but she actually ruined me in a way; she was so perfect that I can never be satisfied with anyone else, because she made everyone else hideous, stupid, and hateful by comparison.''

``Or you could get married to help the other person.''

``Way too much of an investment for one person I don't care for.''
