\chapter{Pain}

So when the treasure ship arrived, I took all the plunder we had acquired (which accounted to none at all), and boarded the ship.
The shock and shame on every shipman's face embarrassed me. I knew they were thinking I was a terrible king and that they had sailed all this way for nought.

``Men,'' I said to them, ``as you have probably noticed, there is no spoils this month. We have been thwarted by a ghost on many occasions; he's faster than our horses and very cunning.
But fear not, Twizwa has assured me that by the time we return, the ghost shall be trapped in the town of Pwiibaa in a device that shall immobolize him.
As for me, I'm taking a much needed vacation from this whole ordeal to make sure all is well in our fair land of Zinodwo.''

We sank a couple of pirate ships (the treasure ship is a much envied target) before arriving home at the port of Shiizee\footnote{Fo\-bwa for ``Water hole.''}. The dock is surrounded by cliffs on three sides which allows archers and catapult men to easilly defend it. Again I was bombarded with lots of questions about the lack of the treasure.

Exhausted and sick, I suffered for the two day cart ride to Zinodwo's capital; unable to sleep on account of my pain. Surely this is how I'll die, vomitting out the window of this cart. My head felt light and my stomach heavy. Was I to die? To my relief I finally passed out.

I woke up in my palace. Still fairly sick, we wondered if these would be my last moments. No! I would not die without doing so in peace, and in order for that I needed to put to rest the nagging doubt in my mind: I needed to see that my country was well off and prosperous and not miserable and poor as that beggar had claimed. I called for my attendant Waterfall\footnote{\emph{Baabiive} in Fobwa.} and asked her to arrange a brief tour of the country going through three of our main cities for a week hence. This done, I laid in my bed and stared at the landscape through my purple curtain. (In the state I was in, I was too lazy to move the curtain, and didn't wish to call upon anyone to attend to it.) So I stared at the curtain (when I was not sleeping) for the remainder of the week as my health gradually returned to me. And with the arrival of my health came the dismissal of my fears. How ever did that sickness put me into a stupor into which we actually almost believed the lies spewed by an uneducated uninformed beggar? There's no reason that a country, being well provided for with a steady income of treasure every month, should ever see the problems one finds in the abject poor places such as Kaaji.

Nevertheless, the people expected us, and it would do no good to displease the people, who at a moments notice could take over the nation by force if they were not satisfied; so we embarked on our tour. 

We stopped at each city and each of the mayors had a feast prepared of some of their best food, beef, oranges, and well aged wine. The streets were all clean with no beggars to be seen. The people had many a parade in each town and I was very impressed by their prosperity; that beggar had lied to me! So I stormed back to my palace and was about to kill the beggar and to make him suffer long.

``I just completed my tour of the country. All is well, the people are joyous and have plenty. You decieved me.'' We said.

``I what?!'' Asked the beggar who was now in charge of the treasury. ``What ever did I tell you?''

``You don't remember?'' I asked incredulously.

``Oh king, I say a lot of things, I can't be expected to account for all of it.''

``You said that Zinodwo was full of beggars!''

``I said that? Oh why I was so right. Now that I see it for myself there's not a doubt.''

``I saw none of that. Nothing, no prostitution, no gambling, no drunkery, no begging, nothing. Everyone was elegantly attired as well.'' We said.

``Of course not,'' explained the beggar, ``when a king comes, the people prepare themselves, they clean up the streets, they cast out the beggars, (or dress them up) and they put up facades where their shacks are in shambles. Then they set up festivals and parades and they--''

``So if I put on peasants clothes, forsake my entourage, and arrive unannounced I shall see the real Zinodwo?''

``I guarantee it.'' Said the beggar.

``That would be a disgrace to the crown. I think that you're only here to make a fool of me. I have not ascended to the heights of the throne only to lose it all chasing after your baseless claims!'' So I cast the beggar into my dungeon and went to admire my treasure.\footnote{Of course none of this exchange happens, this is a corruption of the monologue Mwefu has in the original where he comes to essentially the same conclusion.}

\tbreak

However, when day broke, I found that the nauseousness of before had returned with no chance of mitigation. I again fell into the stupor where I wished not to be ignorant of the plight of my people. I told Waterfall that I wished not to be disturbed. Then putting on some servants clothes, I snuck\footnote{sneaked} out of my palace by the secret passage known only to myself and the architect. (Don't think that I'll go into detail of that because to do so would be to open myself up to an assassination; not that that is much of a concern at this moment.)

We walked alone for about two miles until we found a village. Their houses were thatch huts\footnote{Scholars think that the term ``mud holes'' is truer to the original Fo\-bwa phrase.}, barely keeping out the sun. I saw that their fields lay fallow and hadn't been cultivated in years. The people pounced upon me to beg and told me how they were all starving. How could this be? So I gave them all the money I carried with me\footnote{about 6 gold coins}.

But now I faced another problem, I was hungered. So I walked yet another mile and found a market. The combination of sickness and hunger weighed upon me as I demanded some meat from butcher.

``Not so fast!'' Said the butcher, ``You beggars can't just come up to me demanding food, you need money to pay for it. But as usual you already spent it on exotic spices\footnote{Probably opium or cinnamon} and festivities.''

``I am the king of Zinodwo and I need food and drink.'' We said.

``Well, if that be so, where's your assemblage of guards? Where's your robes, your infinite supply of gold?''

I had a fail-proof way to prove myself.

``Show me the coin you'd want to receive for a cut of steak.'' I said wearily.

``Don't try to pull a fast one on me.'' Said the butcher as he waved a silver coin in the air.

``See that picture, and that signature?! I swear. They're mine! I am the king!''

``There is a little bit of resemblance ain't there.'' Said the butcher as he hastily put the coin back in his pocket. ``And I dare say you could probably forge the inscription if given a chance. But all logic points to your not being the king.''

``I'm in disguise. I wanted to see the country as it really--''

At that moment the butcher knocked me to the ground and tied my hands and legs. I would have been able to beat him any other time, but my sickness, combined with fatigue, thirst, and hunger, made me powerless.

``Now the king's an excellent fighter they say.'' Said the butcher. ``So good there's not one man alive who could take him. Fact, that's how he became king. So I say, as I have just tied you up that you've failed ev'ry test. There's probably a reward out on your head I shouldn't wonder, despite as bad as your impersonation was.''

``I swear I could have killed you.'' I said, ``If it were not for the extreme state of sickness I am suffering.''

``Oh you're sick alright. Sick of the mind.'' And with that the butcher closed up his shop, threw me in a cart and hauled me back to the palace.

\tbreak

There was a brief trial where all the evidence was presented and all my subjects agreed that it couldn't possibly be me. I was merely a shadow of my former self; I had not my vigor, not my kingly clothes, and my voice creaked from thirst. I had none of the qualities of a king. For all they knew, the king wished not to be disturbed and he hadn't gone out. I could have explained myself. I could have told of the state of the country and the poverty caused by my gifts of treasure. No, I couldn't. To do so would be humiliating. I had ruined two countries, I had lost a fight, I had gone behind my servants' back. No, to explain myself would mean that I'd probably be killed as a traitor, whereas to stay silent would mean that I'd probably only be locked up as a mad man. So they all agreed that this was not the king, all evidence pointed to it.

They congratulated the butcher on his capture and gave him 30 gold coins. Then they threw me into my own dungeon.

``So I suppose this means I'm right.'' Said a voice from a dark corner of the cell.

``Right about what? Who are you?'' I asked.

``Oh, I used to be real important. I was once second in command of the whole country. I--''

``That can't be,'' I interrupted, ``Bwaa was put to death. I saw the action myself.''

``Heads are easily reattached.''

``He wasn't beheaded though, he was hind and quartered\footnote{This malapropism is atrocious. Pacoitz mixed-up the term \emph{hindquarters} with \emph{drawn and quartered}.}.''

The voice laughed. And the man to which it belonged crawled out of his corner; it was the beggar.\footnote{You probably guessed that this whole idiotic scene with the beggar was not in the original. Bwaa really did die, and the beggar is not him! Pacoitz is once again abusing his power as a translator.}

``That's why I'm crippled.'' Said the man.\footnote{I cannot stress enough how much Pacoitz' obsessive fascination with the beggar is ruining the story.}

``So all of this is your elaborate revenge upon me then?''

``More or less, yes.''

For the next two days I listened to his rambling and my heart grew heavier and heavier. I'd destroyed my country, destroyed myself, and now I had to listen to my ex-second in command speak unincessantly. I could kill him, of course I could; but then I'd suffer the death penalty for sure or be moved to a cell that allowed no chance of escape.
