\chapter{Robert Graft Finishes the Story}
\emph{Whinery Press} does not have any other translations of \emph{The Fall of King Mwe\-fu} licensed for use in this book, so I have paraphrased the parts of the story which the reader has been deprived of because Pa\-co\-itz left them out.

\begin{flushright}
\textsc{
Robert Graft,\\
Editor at \emph{Whinery Press}}
\end{flushright}

\tbreak

So I trained Naa\-zwa\-to. I purchased a book on fighting at Naa\-zwa\-to's request, however, upon reading it, I found that the contents themselves were pretty near worthless; pages and pages of names and dates and battles. There wasn't a technique or a strategy espoused in the entire volume which would be useful; all the better -- I would substitute my words for its own.

While pretending that I was reading the lessons out of the book, I taught Naa\-zwa\-to many skills such as: sword disarming, kickboxing, and various dodging maneuvers.  We also went to the tailor and the blacksmith to have Naa\-zwa\-to's armor properly fitted.

``I don't understand it,'' Cried the tailor, ``your armor is all different sizes. Your mail shirt is too baggy, your breastplate is too tight, and your boots are just wooden blocks.''

``How dare you! I -- I --'' Said Naa\-zwa\-to.

``They were on sale.'' I said, interrupting him.

``The whole set would cost more to fix than to make new.'' Said the tailor.

``How much?'' Asked Naa\-zwa\-to.

``40 gold units.'' 

``And for new?''

``20 gold units.'' So because Naa\-zwa\-to only had 5 gold units, we left. On the way out we were stopped by an old woman.

``Come with me.'' She said. The old lady took us to an old house in the woods on the border of the lead hills.

``You don't want metal armor, it's too heavy and easy to cut and deform.'' She said.

``Then pray tell, what could we possibly want? Leather?!'' Said Naa\-zwa\-to.

``No.'' Said the old woman followed by a fit of laughter, ``You want wood.''

``But wood is flammable and fragile.'' Said I.

``Not all wood. You've heard of iron wood? Well that won't do. I'm the only worker of something much better, diamond wood.''
She showed us to a small grove of a dozen trees with glittering bark. The old woman handed Naa\-zwa\-to an ax and bid him to fell one of the trees. He swung the ax at the tree, but the strike left the tree unscratched and Naa\-zwa\-to's hands bleeding and his mouth cursing. The old woman laughed,
``It's funny every time. See? Iron can't harm this wood.'' 

``Then what can?!'' Demanded Naa\-zwa\-to still rolling on the ground.

``Oh I won't tell you, but I will make you a suit of it if you can bring me three things --''

``I hate it when this happens.'' I said aside to Naa\-zwa\-to.

``First I need an orange pear, a shoe from the most beautiful woman in Shiizee and a lock of Mwe\-fu's hair.''

``Why do you need that garbage?'' Asked Naa\-zwa\-to, ``Are you a witch?''

``No.'' She said laughing again, ``I'm just sentimental.''

So the two of us departed to find those things. We found the pear from an exotic fruit merchant -- It was mostly orange. We inquired about and found that the most beautiful woman was actually a cobbler, so we tried to buy a shoe from her. But she protested, ``Just one shoe? I can see by the boxes you wear that you need at least a pair.''\footnote{I let my wife read this manuscript. She hated it!
She asked me why my writing was so much ``worse'' than Pa\-co\-itz' -- I had to explain to her that Pa\-co\-itz fabricates content and that I was staying true to the source material and that my writing was better no matter how you look at it. But even so, she said that she did not care and that she preferred that I would keep my editorial notes out of it.

Well, I can make stuff up too, in fact I will, I'll be a better bad translator that Pa\-co\-itz could ever even dream to be.}

\chapter{Robert Graft Takes Liberties With The Text}
``I can clearly see by the shoddy make of your shoes that you need a whole new pair.'' Said the woman who was not in actuality very beautiful.

``Pshaw.'' Said Mwe\-fu, ``We already bought a pear from the fruit merchant.''\footnote{Goodness, isn't that pun stupendous? It really helps one to be immersed in the story's setting.}

``Oh, my apologies then.'' Said the cobbler rather flustered as she handed the two men a size six leather boot, ``This should work then \ldots on the house.''

``Well to be honest,'' Said Mwe\-fu, ``the house is rather too large for this shoe, particularly the big house which is where I'll likely be going.''

``Ignore him.'' Chimed in Naa\-zwa\-to, ``He's going to be executed, I doubt he'll spend any time in jail.''

``Then that's the abomination Mwe\-fu.'' Gasped the woman running out of breath and passing out. (Corsets are an infernal contraption and I've never witnessed a woman faint who wasn't wearing one.)

``You don't think then that we could simply use a lock of your hair?'' Said Naa\-zwa\-to.

``We could, but I doubt it'd keep any serious thief out.'' Mwe\-fu replied. (The reader should notice that this is all my own fancy now and that I switched the narrator from Mwe\-fu to myself, just because I can. In the words of my wife, ``Who cares where the original story went? I just want to enjoy myself.'' Well, I can write an entertaining story, never you mind about accuracy.)

So Naa\-zwa\-to cut a chunk of Mwe\-fu's hair and they both returned to the old woman who was a self-proclaimed expert in diamond-wood.

``Bah!'' Cried the old lady, ``This boot won't fit on my house! This is not a pair of oranges! And anyone can see from the bald-spot on your armor bearer's head that these hairs are his.''

So she expelled the two men from her house.\footnote{How's that for a deviation from the original? The old woman was supposed to have made Naa\-zwa\-to the armor, but I changed it because I'm a bad translator.}

Well because the two had wasted their time, (just like you did when reading this book) they rushed to the castle to register for the tournament.

``I didn't need that decrapet\footnote{See, I can spell words wrong like Pa\-co\-itz too, does that me a better writer, darling?} armor anyway, the power is inside me.''

``Sure it is.'' Mocked Goat, AKA Mwe\-fu, ``The problem is getting it out without hurting yourself.''

``Most indububabblabla -- I'll never be pompous enough to use that word.''

\tbreak

So they took a number and sat down in the bleachers.\footnote{I just can't do it! I was going to make a pun about the benches being used to remove dye from fabric, but I can't. Maybe that's why Pa\-co\-itz went mad because he doesn't feel guilty about writing so poorly.} The tournament would not start for another hour; so Mwe\-fu gave Twi\-zwa that failed poem he acquired from the beggar.

``This poem is pretty good -- you didn't write this!'' Twi\-zwa said to Mwe\-fu, ``The rotational poetry is quite refined, every rotation is a continuation of -- oh dear! This is broken -- it doesn't work right. I can fix it. No problem.'' Twi\-zwa then furrowed his brow and was lost deep in thought. ``This should buy us some time.'' Thought Mwe\-fu.

The former king recognized most of the people who registered for the fight, and from the glances they gave him, they must have recognized him too. However there was an old man who was very tall and fairly fat. What was left of his white hair hung down to his shoulders and his curly white beard hung down at his chest. Overall his skin was blotchy and scarred as if it couldn't quite decide whether the man it belonged to was light or dark in complexion. He stood nearly seven foot tall. Perhaps he had been a great fighter in his prime maybe 40 or 50 years prior.

``Who is this man!'' Demanded the king from his throne as the old man approached him, ``Twi\-zwa find out! Stop messing with those stupid poems.'' Hurt by the insult, Twi\-zwa began to thumb through the annals of Zi\-no\-dwo. The old man handed the king a piece of paper which told about the leader of an independent merchant fleet whose name was Captain Seaweed. It had a poorly written poem about the sea on the back so Twi\-zwa snatched it up and tried to fix that poem too.

``That's Captain Seaweed then,'' Said the king, ``he was king of Zi\-no\-dwo 50 years ago.''

``If you hadn't let things get so bad I wouldn't have had to come back.'' Said Captain Seaweed.

``You're not serious, you're old and fat. You can't win.''

``Oh yeah, you're real tough. Killing women and children and robbing your own country. In order to win this tournament you will have to defeat myself, which will be impossible due to the size of my feet. And you'll also have to beat that man over there,'' He pointed at Naa\-zwa\-to, ``who I have no idea who he is, but Mwe\-fu is his armor-bearer, so he must be amazing. Don't feel insecure due to your lack of skill or strength though, you might get really lucky.'' Captain Seaweed leaned against a young tree and acted like he was going to snap it in two, but he must not have been strong enough.

``Arrogant washed-up fool.'' Muttered the monarch as he meted out mutton to a mutt he had met that morn.\footnote{Wow, doesn't that alliteration just make the story so much better? English teachers will be singing my praise.}

\tbreak

The tournament manager blew the trumpet and called Naa\-zwa\-to and some farmer to fight. Just to clarify, and yes, I'm not even bothering to look this up but just asserting my own opinion as fact, the fights are done with only wooden weapons to prevent fatal injury to great fighters; people still die sometimes.

A farmer gave a good fight and had almost knocked Naa\-zwa\-to out of the ring with his club when Mwe\-fu yelled, ``Kick his right knee!'' The farmer then panicked and Naa\-zwa\-to knocked him over the railing thus winning the fight. Mwe\-fu had fought the farmer in the tournament after Waterfall and Vwu\-mwaa tried to supplant his rule; at that time, Mwe\-fu had hurt the farmer's right leg and likely it was still not fully healed. 

Next the current king went up against the beggar. (Why not? If Pa\-co\-itz can insert him into extra situations that don't make sense, why can't I?)

``Why won't you stand up to fight me?'' Asked the king.

``I'm a cripple, you blathering moron.'' Responded the beggar.

``Then I suppose I win by default. What was even the point of --'' The king was interrupted by a blow to his helmet and fell to the ground.

``I can throw rocks just fine from down here.'' Said the beggar as he crawled towards the king.

``Twi\-zwa! Find out who this fool is and tell me how to beat him!''

But instead of listening to the king, Twi\-zwa was now mulling over what seemed to be a third poem, possibly given to him by the beggar in order to distract him.

The king got up, and the beggar hurled another rock, which hit the king's hand and made him drop his club. The beggar then grabbed the club and struck the king's leg.

``Oww! I was going easy on you, but no more.'' Said the king as he grabbed the beggar by the legs, spun him around, and tossed him out of the ring.

``Watch it! You could have broke my neck and made me crippled!'' Shouted the beggar.

``But you're already crippled.'' Said the king.

``He's a paraplegic, he could have become a quadriplegic.'' Muttered Twi\-zwa, ``It probably would be for the better though, considering his awful poetry and his penmanship that sails off the edge of the page.''

Next Captain Seaweed went up against the king's brother Carl\footnote{Doesn't even fit the phonology of the Fobwa language and I don't care.}.
Carl swung his club at Captain Seaweed so hard that it snapped. Captain Seaweed stumbled and slowly layed down. Carl began kicking the large old man.

``You're going to join a fight and not even fight back?!'' Asked Carl. Captain Seaweed beckoned Carl over, and whispered in his ear something that no one else heard. Carl's face immediately turned white as snow and he screamed and threw himself over the railing. Seaweed was thus the winner.

Next the king went against a wild man who often wrestled the beasts -- but man is no beast, and the king disabled him with ten hits of his club. After that he tossed his unconscious body over the fence.

Then Captain Seaweed fought Naa\-zwa\-to, or rather Naa\-zwa\-to fought him, for the captain didn't lift a finger to fight back. But Naa\-zwa\-to began to tire.

``You can't buy me like you bought Carl.'' Said Naa\-zwa\-to out of breath.

``That's not what happened. I told him I was thinking about hitting back. I hit hard -- everyone knows it.'' This was followed by Seaweed punching Naa\-zwa\-to which knocked him to the ground and shattered his wooden breastplate.

``Here's a week's wages.'' Said the captain as he dropped some coins, one at a time, onto Naa\-zwa\-to, ``Buy yourself some decent armor. This isn't even a fair fight. Honestly I feel bad.''

``You're not even wearing armor yourself.'' Said Mwe\-fu to Seaweed.

``Shut up. He's disadvantaged enough as is.'' Said Seaweed. Then he picked Naa\-zwa\-to off the ground and Naa\-zwa\-to thrashed like an angry cat. Seaweed then walked to the railing and gently set Naa\-zwa\-to down on the other side.

``That wasn't a fair fight!'' Screamed Naa\-zwa\-to to the king, ``You put me against him so you wouldn't have to fight me.''

``True enough.'' Agreed Seaweed, ``But now I'm his problem.'' The king began to panic and started muttering something to Twi\-zwa who was still working on those poems.

``Give the boy a suit of armor.'' Said Seaweed, ``Let him fight me again. You wouldn't want to fight me before I'm fully tired.''

``I'm not a boy. I'm the greatest bounty hunter in Zi\-no\-dwo.'' Said Naa\-zwa\-to taking the suit of armor that one of the king's servants gave him; it was made of quality steel. He put it on and got in the ring to challenge the old captain again.

Maybe it was due to the confidence of a new suit of armor, but Naa\-zwa\-to fought much better. He struck the captain with a club and the captain struck back with an open hand, they exchanged blows for a while. Finally it looked like Captain Seaweed was beginning to tire as he stumbled and grabbed the railing. Naa\-zwa\-to beat Seaweed to the ground and grabbed his feet to drag him out of the ring.

``You should have thought about how you were going to get me out of the ring. I stood right by it to make it easy for you even.'' Said the captain kicking Naa\-zwa\-to over the fence with his powerful legs.
Seaweed was the victor, but no one was happy.

``I hoped you would have put up more of a fight.'' Complained the captain, ``Who's next on the bracket?''

``We can't let Captain Seaweed win.'' Muttered the king to himself.

``Don't you worry, there's still more people I can fight, Mr. King.''

``There is no one.'' Said Twi\-zwa. But Seaweed threw two daggers at Mwe\-fu who gracefully snatched them out of the air before they could hit him. 

``But Mwe\-fu is not eligible --'' Said the king. Twi\-zwa immediately shushed him, ``Don't interrupt your enemy while he's making a mistake.'' Seaweed nodded in agreement and smiled.

Mwe\-fu then put on Naa\-zwa\-to's borrowed armor.

``All this time you were the real Mwe\-fu.'' Cried Naa\-zwa\-to, ``You really are a snake.''

``He's a snake? What do I get to be then?'' Interrupted Seaweed.

``The loser I hope.''

``I don't think I could be so lucky. That would make the king the winner by default though.''

So Mwe\-fu and Seaweed fought, but rather slowly, Mwe\-fu with his club, and Seaweed with his bare hands.
Each blow was perfectly blocked by the other. After getting a feel for Seaweed's strategies, Mwe\-fu sped up and hit Seaweed in the chest and head many times.

``You're holding back?'' Asked Mwe\-fu.

``Always.''

Mwe\-fu feigned to hit Seaweed, but the captain didn't realize it was a bluff so he put his hand out to block, and instead of hitting the club, Seaweed hit Mwe\-fu and he crashed through the railing.

``Oops.'' Said Seaweed, ``You moved so fast I missed my parry. It was a fun fight.'' But Mwe\-fu wheezed and didn't reply.

``To challenge that old brute to a fight is suicide.'' Said Twi\-zwa to the king.

``I just got the crown, I'm not losing it to a withered old man.'' Said the king jumping into the ring, ``Why are you even here you failed captain, why aren't you out at sea smuggling apricots or something?''

``Oh believe me, I'd rather be doing that, but I gave it up. Or they gave me up, any way, I have nothing else to do.''

``I could make you second in command, you could lead my armies, surely we could find something for you.'' Said the king shaking in fear.

``No. I think everyone has had enough of you. Please, pick up a real sword.'' The king traded his club for a iron sword. The fight began. The king swung his sword at Captain Seaweed, but Seaweed slowly sidestepped it. The king swung again and missed, then the captain grabbed hold of the king's empty hand and squeezed it. He crushed his hand so hard that the king dropped the sword out of his other hand and he fell to his knees on the ground.

``Won't you have mercy on me?'' He cried.

``When have you once shown mercy?'' Said Seaweed squeezing the king's hand yet harder.

``It's hard to think when you're breaking my hand.''


``Very well.'' Replied Seaweed grabbing the king's wrist instead. The king reached for the captains neck with his free hand but Seaweed squeezed his captured wrist until a crack was heard. The king let out a scream and went limp.

``I've been more than fair.'' Said Seaweed, whipping the king's body out of the ring like a wet towel.
