\chapter{The Imposter}

There in my own prison I despaired of life -- was there none among my own court who knew me?

The first night in the dungeon came slowly. All I could hear was Bwaa's incessant rambling and heckling. But then I heard the creaking of giant steel doors and the fall of footsteps; this was accompanied by a flickering red-green light.\footnote{In Fobwa there are only three colors: red, green, and blue (not unlike the RGB system used in televisions today). So the colors when mentioned for the same subject combined rather than remain independent, so \emph{red-green} should be rendered as \emph{yellow}.}
The light, though dim, seemed as bright as the morning sun by comparison to the dank prison.

The persons carrying the lantern opened my cell.

``Ha! I knew justice would come to my aid.'' Said the beggar.

``No, you fool.'' Said a voice which I immediately recognized as Waterfall, my servant. ``We've come to relocate the impostor.''

``But we are the king!'' I protested.

``Keep up the act.'' Said Vwu\-mwaa, who evi\-dent\-ially\footnote{Yes, this is spelled wrong. My senior editor will not allow me to change any of Pa\-co\-itz' text even if I believe there are terrible problems with it.} was there also.
They placed a sack over my head and led me out of the prison; whispering amongst themselves as they went. As soon as we were out of the dungeon, they slipped the bag off my face, and we continued to walk till we were to the Lead Hills; we sat down in a valley there between two gigantic rocks.

``How am I to die?'' I said, interrupting their secret consul fearing that my execution was imminent.

``Who knows?'' Replied Waterfall, less as a question and more as if to say that she didn't see my death coming anytime soon.

``Listen to our cause and you may not die ever.'' Said Vwu\-mwaa.

``Vwu\-mwaa! I hardly think that immortality as such is attainable.'' Waterfall said.

``Well if it were, kingship would be the way.''\footnote{Said Vwu\-mwaa.}

``Pray tell, what are you proposing?'' I asked.

``To supplant the current leadership and replace it with you of course.'' Replied Waterfall.

``The resemblance is sufficient for all needs and purposes.'' Vwu\-mwaa explained. I saw now that they intended to plant me on the throne thinking I was an impostor who would enact giant favors on their behalf.

``So\ldots'' Vwu\-mwaa continued, ``we make you king, and you pretend to be Mwe\-fu, and give me 1,000 gold coins.''

``For myself,'' Interrupted Waterfall, ``it is enough that you make me privy to all your councils and heed my advice. Refuse or deny us in any way and we will oust you as the fake that you are.''

Without their help I would not have been set free; so I complied.

\tbreak

``Traitor! Impostor!'' Said Twi\-zwa once again interrupting my story to berate me, ``You thought you could hide the truth by lying, but instead you revealed it! You never were Mwe\-fu, you replaced him on that day and the rest is a mass of half-truths.''

``Twi\-zwa!'' I interjected (his name had almost become a curse in my mind), ``If I were not Mwe\-fu, how ever did I, last week slay 30 men by myself when we were ambushed by the Hii\-kaga\footnote{Fast dark blues}.

``So what? You just happen to be a fighter on par (almost) with Mwe\-fu, that's not impossible; but it does not prove you are him.''

``That's ridiculous, what are the chances that I'm that skilled of a warrior, have Mwe\-fu's face (his voice even), yet am not Mwe\-fu? Even two of those being true is unlikely, but three?''

``Well then,'' Said one of my soldiers, ``carry on.''

\tbreak

``Wait, what about the old king'' I asked.

``Our bounty hunter assures us he's already been disposed of.'' Said Vwu\-mwaa. They didn't tell me who their bounty hunter was, but I knew that whoever they hired was an opportunistic liar.

So they released me from my bonds and returned me to my throne. After a week of listening to Waterfall's and Vwu\-mwaa's demands, I'd had enough and arranged a tournament to prove beyond a doubt that I was Mwe\-fu. Once I had proved myself, Waterfall and Vwu\-mwaa would have nothing to blackmail me with.\footnote{How pathetic, every school boy knows not to end a sentence with a preposition.} So I dominated every fight and cemented my sovereignty. And Waterfall and Vwu\-mwaa were hanged as traitors.

I had portraits of myself painted and my scars and freckles documented so that never again would my throne be denied me. Though I never confessed (until now) that I had been mistaken for an impostor and imprisoned.

Being king again was most relaxing; I went and admired my treasury -- gold, silver, topaz, onyx, jade,\footnote{Actually \emph{emerald}} and countless other precious stones. (Though Vwu\-mwaa claimed to have numbered and sorted them, he's as crooked as a rubber ruler.)\footnote{This rubber ruler nonsense is so clich\'{e} and doesn't fit at all with the setting.} The treasure shipments kept arriving and were distributed by Pine\-cone\footnote{No name was given in the original, this is another Pa\-co\-itz fabrication.}, my new treasurer. I had considered stopping the raid entirely -- but the people like being given an unearned income; I felt chaos would follow and they'd start a revolution if I was to stop supplying them.

After some time, I received a letter from Twi\-zwa. It was very poetic and told of the success his trap had on the ghost.

\begin{quote}``My lord, we have captured the wooden-armored rebel. We dug pits and covered them up with grass; then when the ghost was walking towards our plunder room, he fell into one of the holes. My men heard it and quickly closed it up so that he could not escape. Two days passed and out from the hole a voice cried for food and water. But why would a ghost need any of that? So we did not oblige him. After two more days he died. And do you know what? When the coroner was going through his belongings, do you know what he found? Nothing really; but it turned out that the ghost wasn't really a ghost, hence why it died. Woe, it was Paa\-vo. He had fooled us all and was subverting your dominion. What a clever spy! What a nuisance!''
\end{quote}

I immediately cast the letter into my fire. Paa\-vo was dead. There was no escaping or denying it. Nevertheless, he cheated death once, perhaps he could do it again. So the next day, I departed for Ka\-ji to see if perhaps Paa\-vo was still alive. I sure hoped he was.
